### 2024-10-10 Manuscript/main_ecography_R1.tex
Update main_ecography_R1.tex

\begin{figure}[!htbp]
\centering
   \includegraphics[width=0.5\textwidth]{Figures/simulation_protocol.pdf}
\caption{\scriptsize{Illustration of the simulation protocol used in this paper.
A) we simulated a pure birth-tree with a trait evolving under a Brownian Motion process until reaching 200 observations resulting a trait space of 2, 4, or 8 dimensions.
The first plot on row A illustrates one such simulation in one dimensions through time (with time on the horizontal axis and trait value for one dimension on the vertical axis).
The second plot on the same row shows the same results but with 2 dimensions of the trait represented here.
We then applied different stressors to the resulting trait space.
We represent the observations removed by the stressors in blue and the ones kept in the trait space in orange.
The first column (histograms) illustrates the distribution of observations in one dimension of the 2D, 4D or 8D traits with the overlap between the removed (blue) and kept (orange) observations in brown (note we did not measure any metric on 1D spaces).
The second column illustrate the trait in 2 dimensions.
For traits 
We did not illustrate the distributions in 4 or 8 dimensions here.
We used the following stressors:
B) \textbf{null mechanism}: randomly removing a proportion of the observations;
C) \textbf{equalising mechanism}: removing observations on the edge of the distribution;
D) \textbf{facilitation mechanism}: removing observations to reduce the distance between pairs of observations (increasing local density; decreasing evenness);
E) \textbf{observations mechanism}: removing observations on one extreme of the distribution;
F) \textbf{competition mechanism}: proportionally removing observations on the centre of the distribution (``flattening the curve'').}}
\label{Fig:simulations}
\end{figure}
\bigskip

>>>>

\begin{figure}[!htbp]
\centering
   \includegraphics[width=0.5\textwidth]{Figures/simulation_protocol.pdf}
\caption{\scriptsize{Illustration of the simulation protocol used in this paper.
A) we simulated a pure birth-tree with a trait evolving under a Brownian Motion process until reaching 200 observations resulting a trait space of 2, 4, or 8 dimensions.
The first plot on row A illustrates one such simulation in one dimensions through time (with time on the horizontal axis and trait value for one dimension on the vertical axis).
The second plot on the same row shows the same results but with 2 dimensions of the trait represented here.
We then applied different stressors to the resulting trait space.
We represent the observations removed by the stressors in blue and the ones kept in the trait space in orange.
The first column (histograms) illustrates the distribution of observations in one dimension of the 2D, 4D or 8D traits with the overlap between the removed (blue) and kept (orange) observations in brown (note we did not measure any metric on 1D spaces).
The second column illustrate the trait in 2 dimensions.
We did not illustrate the data beyond 2 dimensions for traits in 4 or 8 dimensions.
We used the following stressors:
B) \textbf{null mechanism}: randomly removing a proportion of the observations;
C) \textbf{approximating equalising mechanism}: removing observations on the edge of the distribution;
D) \textbf{approximating facilitation mechanism}: removing observations to reduce the distance between pairs of observations (increasing local density; decreasing evenness);
E) \textbf{approximating filtering mechanism}: removing observations on one extreme of the distribution;
F) \textbf{approximating competition mechanism}: proportionally removing observations on the centre of the distribution (``flattening the curve'').}}
\label{Fig:simulations}
\end{figure}
\bigskip
